### 2015-05-06 papers/histogram/thesis/thesis.tex
first completed draft of methods section

@@

The partition function at $T=T_0$ for simulations with canonical
weights is
\begin{align}
  \tilde Z\p{T_0}=\sum_E\tilde D\p{E}e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{w\p{E}}~e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{e^{-E/kT_0}}~e^{-E/kT_0}=\sum_EH\p{E},
  \label{Z_canonical}
\end{align}
and the value of a thermodynamic property $X\p{T_0}$
\begin{align}
  X\p{T_0}=\f1{\tilde Z\p{T_0}}\sum_E\bk{X}_E\tilde D\p{E}e^{-E/kT_0}
  =\f{\sum_E\bk{X}_EH\p{E}}{\sum_EH\p{E}},
  \label{eq:X_canonical}
\end{align}
where $\bk{X}_E$ is the mean value of $X$ at the energy $E$. The
simplifications in in (\ref{Z_canonical}) and (\ref{eq:X_canonical}),
which have no explicit dependence on $T_0$, occur because canonical
Monte Carlo simulations sample energies in proportion to the
distribution (over energy) of microstates at a temperature of $T_0$.
Canonical Monte Carlo simulations can therefore fail to sufficiently
sample energies which are important (i.e. energies with a
non-negligible state probability density) at different
temperatures. As a consequence, such simulations should not be used to
determine properties $X\p{T\ne T_0}$, and are thus referred to as
``fixed temperature'' simulations.

@@

Due to these problems, we will not use canonical weights alone to
study the square-well fluid. We will, however, use canonical weights
for portions of all weight arrays, which we discuss in Section
\ref{sec:energy_range}.

@@

Given the expression for $\bk{X}_T$ in (\ref{eq:XT}), sufficient
accumulation of statistics on $\bk{X}_E$ at all available energies in
principle allows one to determine $\bk{X}_T$ for any temperature
$T$. In practice, the density of states can fall off so quickly with
energy that some range of allowable energies is practically
inaccessible via Monte Carlo simulations, biased or otherwise. In such
a case, computing $\bk{X}_T$ to a reasonable degree of accuracy
requires sufficiently sampling the energies at which $\tilde
D\p{E}e^{-E/kT}$ dominates the sum in (\ref{eq:XT}). Section
\ref{sec:energy_range} provides more discussion on this subject,
namely on identifying the energies which are important for computing
system properties at a given temperature.

@@

In our implementation of the simple flat method, we used $u=2$ and
$n_0=L\exp\p{\epsilon/kT_{\t{min}}}$, where $L$ is the number of
energy levels of the given square-well fluid and $T_{\t{min}}$ is a
minimum temperature of interest for the current simulation. The factor
of $L$ appears because initialization time should scale with the range
of energies of the simulated system. If we have twice the number of
energies, we should explore energy space for twice as long. To
estimate $L$, we multiplied the maximum number of spheres $M$ which
fit within a radius of $\lambda\sigma$ of a single sphere on a
face-centered cubic lattice (i.e. the maximum number of spheres with
which a given sphere could interact) by the total number of spheres
$N$, and divided the result by two so as to not double-count
interactions between spheres (so $L=MN/2$). The exponential
$\exp\p{\epsilon/kT_{\t{min}}}$, a Boltzmann factor for two adjacent
energies, appears because lower minimum temperatures of interest
warrant sampling lower energies, which in turn requires simulating for
longer (in step \ref{alg:simple_flat_sim} of Algorithm
\ref{alg:simple_flat}) because these energies have lower state
densities. The introduction of a minimum temperature may seem ad-hoc,
but all simulations in this paper require a choice of minimum
temperature anyways (discussed in Section \ref{sec:energy_range}). In
this paper, we will always use $kT_{\t{min}}=0.2\epsilon$.

@@

The success of Wang-Landau thus relies on some degree of leniency in
the flatness condition, which makes tuning $C\sp{H}$ crucial to the
efficient and effective implementation of this method. Some previous
works\cite{wang_landau} suggest that $C\sp{H}$ should be made as
stringent as possible, cautioning only that some simulations might not
satisfy too strict of a flatness condition in any reasonable amount of
time. These works fail to recognize the reliance of Wang-Landau on the
{\it failure} of $C\sp{H}$ to enforce a perfectly flat histogram. A
commonly suggested flatness condition is that the minimum histogram
value be at least some fixed proportion of the mean histogram value,
i.e. $C\sp{H}:\min\sp{H\p{E}}\ge x\bk{H}_E$, and several papers report
using $x=0.95$. We used the same condition with $x=0.25$.

@@

At equilibrium with a flat histogram, meaning $n$ is constant, the
down-going walker current $j\p{E}$ is defined in terms of the
diffusivity $\alpha\p{E}$ by
\begin{align}
  j=-\alpha\f{dn_+}{dE}.
  \label{eq:walker_current_definition}
\end{align}
This identity can be taken as the definition of the walker diffusivity
$\alpha$, which is the independent of the label we have assigned any
given walker. Substituting $n_+=fn$,
\begin{align}
  j=-\alpha\p{n\f{df}{dE}+f\f{dn}{dE}}=-\alpha n\f{df}{dE},
  \label{eq:walker_current}
\end{align}
where a constant $n$ means $dn/dE=0$. We can rearrange
(\ref{eq:walker_current}) and integrate over the energy range as
\begin{align}
  \int_{f=f\p{E_-}}^{f\p{E_+}}\f{df}{j}=-\int_{E=E_-}^{E_+}\f{dE}{\alpha
    n}.
  \label{eq:walker_current_integral_setup}
\end{align}
At equilibrium, the number of down-going walkers $n_+\p{E}$ at any
given energy $E$ is constant with time, which means that the walker
flux $j\p{E}$ must be constant with energy. We can therefore evaluate
one of the integrals in (\ref{eq:walker_current_integral_setup}) to
get
\begin{align}
  \f1{\abs j}=\int_{E=E_-}^{E_+}\f{dE}{\alpha n}.
  \label{eq:walker_current_integral}
\end{align}

@@

Throughout the discussion and development of histogram methods, we
have thus far neglected three subjects: initialization end conditions
(i.e. the means by which we decide when an algorithm to construct
weights is finished), the energy range about which we care, and the
minimum temperature $T_{\t{min}}$ which we sometimes make reference
to. The last two of these subjects turn out to be related, as the
minimum temperature $T_{\t{min}}$ chosen for any given simulation
determines the minimum energy of interest.

@@

In general, any initialization routine should sample the entire range
$R=\sp{E_-,E_+}$ before terminating. Furthermore, samples at the end
of initialization should be numerous enough to be statistically
significant.\fixme{include mean sample error?} Given that any samples
of $E_-$ necessarily require first sampling all other energies in $R$
on the way down from $E_+$, this energy ($E_-$) will generally have
the fewest number of samples. As an end condition, one can therefore
enforce some minimum number of optimistic or pessimistic samples at
$E_-$, i.e. $s_o\p{E_-}$ or $s_p\p{E_-}$. A more sophisticated end
condition would be to enforce some minimum value to the mean
fractional error $\bk{\delta_s}_{E,T_{\t{tmin}}}$ in either of the
sample counts $s_o\p{E}$ or $s_p\p{E}$ at the minimum temperature
$T_{\t{min}}$. These mean errors are
\begin{align}
  \bk{\delta_s}_{E,T_{\t{tmin}}}=\bk{s^{-1/2}}_{E,T_{\t{min}}}
  =\sum_Es\p{E}^{-1/2}P\p{E,T_{\t{min}}}
  =\f{\sum_Es\p{E}^{-1/2}D\p{E}e^{-E/kT_{\t{min}}}}
  {\sum_{E'}D\p{E'}e^{-E'/kT_{\t{min}}}},
\end{align}
where we use the fact that the fractional error $\delta_G$ in any
histogram $G$ collected via random Monte Carlo sampling is $G^{-1/2}$.

\subsubsection{Determining the energy range of interest}
\label{sec:energy_range}

While some particular systems, such as the Ising model, have
well-defined and easily determined minimum and maximum energies, the
same is not true of all systems in general.

Histogram methods typically rely on knowledge of the minimum and
maximum energies of the system in question \fixme{how?}, which are
unknown for the square-well fluid. Worse still, some square-well fluid
energies have such an incredibly low density of states that one cannot
reasonably expect to ever observe them via Monte Carlo, biased or
otherwise. As such, we need to identify an energy range of interest,
bounded by minimum and maximum ``important'' energies. \fixme{Rewrite,
  expand}

\fixme{The energy at which the density of states is maximal, i.e. the
  state of maximal entropy, sets an upper bound for the energy range
  in which appropriate weights are not obvious. Explain why.}

\fixme{Determining the minimum important energy is considerably
  trickier. Punchline: we have to choose a minimum temperature of
  interest, $T_{\t{min}}$, and the minimum important energy is the
  energy at which the slope of the density of states is
  $\exp\p{kT_{\t{min}}/\epsilon}/\epsilon$. This condition for the
  minimum important energy is directly related to canonical weights at
  a temperature of $T_{\t{min}}$.}

\fixme{Mention that in all initializations which simulate for some
  time with unchanging weights (i.e. simple flat), the weight array
  should be set to canonical weights below the minimum important
  energy, as soon as it is identified.}

\fixme{Mention that weights should be set to canonical weights below
  the minimum important energy after all initializations.}

@@

\subsection{Implementation and overview}
\label{sec:implementation}

\fixme{Talk about the relative difficulty of implementing each method,
  as well as the relative difficulty of optimizing or tuning each
  method. Free parameters are generally bad, and especially so if they
  come without ``obvious'' or prescribed values. Justify our
  modifications to Wang-Landau by showing that we did not make it
  worse. Include mention of how memory requirements for transition
  matrix Monte Carlo scale poorly with system size, as well as energy
  resolution for systems with continuous energies.}

\subsection{Simulation results and errors}
\label{sec:results_and_errors}

\fixme{Talk about the energy histogram, weights, and density of states
  yielded by the methods. These should all be fairly similar. Talk
  about why this is so.}

@@

@@

\begin{figure}[H]
  \centering
  \caption[Normalized densities of states]{Normalized densities of
    states}
  \label{fig:density_of_states}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \caption[Initialization iterations vs. system size]{Initialization
    iterations vs. system size}
  \label{fig:scaling}
\end{figure}

\fixme{Discuss energy initialization times, sampling rates, and errors
  in computed thermodynamic properties. Explain that errors are given
  relative to a simulation which ran much longer, and talk about how
  we ran that simulation (which method did we use?). Show that all
  methods converge on the same answer as they simulate for longer.}

@@

\begin{figure}[H]
  \centering
  \caption[Initialization iterations vs. data quality]{Initialization
    iterations vs. data quality}
  \label{fig:quality}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Specific internal energy]{Specific internal energy}
  \label{fig:internal_energy}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Specific heat capacity]{Specific heat capacity}
  \label{fig:heat_capacity}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nocite{*} \bibliography{thesis}

>>>>

\fixme{Make all mention of what we do in present, rather than past
  tense}

@@

The partition function at $T=T_0$ for simulations with canonical
weights is
\begin{align}
  \tilde Z\p{T_0}=\sum_E\tilde D\p{E}e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{w\p{E}}~e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{e^{-E/kT_0}}~e^{-E/kT_0}=\sum_EH\p{E},
  \label{Z_canonical}
\end{align}
and the value of a thermodynamic property $X\p{T_0}$
\begin{align}
  X\p{T_0}=\f1{\tilde Z\p{T_0}}\sum_E\bk{X}_E\tilde D\p{E}e^{-E/kT_0}
  =\f{\sum_E\bk{X}_EH\p{E}}{\sum_EH\p{E}},
  \label{eq:X_canonical}
\end{align}
where $\bk{X}_E$ is the mean value of $X$ at the energy $E$. The
simplifications in in (\ref{Z_canonical}) and (\ref{eq:X_canonical}),
which have no explicit dependence on $T_0$, occur because canonical
Monte Carlo simulations sample energies in proportion to the
distribution (over energy) of microstates at a temperature of $T_0$.
Canonical Monte Carlo simulations can therefore fail to sufficiently
sample energies which are important (i.e. energies with a
non-negligible state probability density) at different
temperatures. As a consequence, such simulations should not be used to
determine properties $X\p{T\ne T_0}$, and are thus referred to as
``fixed temperature'' simulations. Incidentally, Metropolis Monte
Carlo simulations can be thought of as infinite-temperature
simulations, as they are equivalent to simulations with canonical
weights
\begin{align}
  w\p{E}=\lim_{T\to\infty}e^{-E/kT}=1.
  \label{eq:inf_temp_weights}
\end{align}
This observation will be used in Section \ref{sec:min_energy} to
identify a maximum energy of interest.

@@

Due to these problems, we will not use canonical weights alone to
study the square-well fluid. We will, however, use canonical weights
for portions of all weight arrays, which we discuss in Section
\ref{sec:min_energy}.

@@

Given the expression for $\bk{X}_T$ in (\ref{eq:XT}), sufficient
accumulation of statistics on $\bk{X}_E$ at all available energies in
principle allows one to determine $\bk{X}_T$ for any temperature
$T$. In practice, the density of states can fall off so quickly with
energy that some range of allowable energies is practically
inaccessible via Monte Carlo simulations, biased or otherwise. In such
a case, computing $\bk{X}_T$ to a reasonable degree of accuracy
requires sufficiently sampling the energies at which $\tilde
D\p{E}e^{-E/kT}$ dominates the sum in (\ref{eq:XT}). Section
\ref{sec:min_energy} discusses identifying the energies which are
important for computing system properties at a given temperature.

@@

In our implementation of the simple flat method, we used $u=2$ and
$n_0=L\exp\p{\epsilon/kT_{\t{min}}}$, where $L$ is the number of
energy levels of the given square-well fluid and $T_{\t{min}}$ is a
minimum temperature of interest for the current simulation. The factor
of $L$ appears because initialization time should scale with the range
of energies of the simulated system. If we have twice the number of
energies, we should explore energy space for twice as long. To
estimate $L$, we multiplied the maximum number of spheres $M$ which
fit within a radius of $\lambda\sigma$ of a single sphere on a
face-centered cubic lattice (i.e. the maximum number of spheres with
which a given sphere could interact) by the total number of spheres
$N$, and divided the result by two so as to not double-count
interactions between spheres (so $L=MN/2$). The exponential
$\exp\p{\epsilon/kT_{\t{min}}}$, a Boltzmann factor for two adjacent
energies, appears because lower minimum temperatures of interest
warrant sampling lower energies, which in turn requires simulating for
longer (in step \ref{alg:simple_flat_sim} of Algorithm
\ref{alg:simple_flat}) because these energies have lower state
densities. The introduction of a minimum temperature may seem ad-hoc,
but all simulations in this paper require a choice of minimum
temperature anyways (discussed in Section \ref{sec:min_energy}). In
this paper, we will always use $kT_{\t{min}}=0.2\epsilon$.

@@

The success of Wang-Landau thus relies on some degree of leniency in
the flatness condition, which makes tuning $C\sp{H}$ crucial to the
efficient and effective implementation of this method. Some previous
works\cite{wang_landau} suggest that $C\sp{H}$ should be made as
stringent as possible, cautioning only that some simulations might not
satisfy too strict of a flatness condition in any reasonable amount of
time. These works fail to recognize the reliance of Wang-Landau on the
{\it failure} of $C\sp{H}$ to enforce a perfectly flat histogram. A
commonly suggested flatness condition is that the minimum histogram
value in some specified range of energies be at least some fixed
proportion of the mean histogram value, i.e.
$C\sp{H}:\min\sp{H\p{E}}\ge x\bk{H}_E$, and several papers report
using $x=0.95$. We used the same condition with $x=0.25$. Determining
the range of energies over which to evaluate $C\sp{H}$ is the subject
of Section \ref{sec:min_energy}.

@@

At equilibrium with a flat histogram, meaning $n$ is constant, the
down-going walker current $j\p{E}$ can be expressed in terms of the
diffusivity $\alpha\p{E}$ by
\begin{align}
  j=-\alpha\f{dn_+}{dE}.
  \label{eq:walker_current_definition}
\end{align}
This identity can be taken as the definition of the walker diffusivity
$\alpha$, which is the independent of the label we have assigned any
given walker. Substituting $n_+=fn$,
\begin{align}
  j=-\alpha\p{n\f{df}{dE}+f\f{dn}{dE}}=-\alpha n\f{df}{dE},
  \label{eq:walker_current}
\end{align}
where a constant $n$ implies $dn/dE=0$. We can rearrange
(\ref{eq:walker_current}) and integrate over the energy range as
\begin{align}
  \int_{f=f\p{E_-}}^{f\p{E_+}}\f{df}{j}=-\int_{E=E_-}^{E_+}\f{dE}{\alpha
    n}.
  \label{eq:walker_current_integral_setup}
\end{align}
At equilibrium, the number of down-going walkers $n_+\p{E}$ at any
given energy $E$ is constant with time, which means that the walker
flux $j\p{E}$ must be constant with energy. We can therefore evaluate
one of the integrals in (\ref{eq:walker_current_integral_setup}) to
get
\begin{align}
  \f1{\abs j}=\int_{E=E_-}^{E_+}\f{dE}{\alpha n}.
  \label{eq:walker_current_integral}
\end{align}

@@

Throughout the discussion and development of histogram methods, we
have thus far neglected a few important subjects:
\begin{enumerate*}
\item initialization end conditions i.e. the means by which we decide
  when an algorithm to construct weights is finished,
\item the minimum temperature $T_{\t{min}}$ which we have sometimes
  mentioned,
\item the energy range over which we are interested in, and
\item what to do with the weight array outside of the energy range of
  interest, or at in which it is not defined.
\end{enumerate*}
The last three of these subjects turn out to be related, as the
minimum temperature $T_{\t{min}}$ chosen for any given simulation
determines the minimum energy $E_-$ of interest, as well as the
weights $w\p{E}$ at energies $E<E_-$.

@@

In general, any initialization routine should sample the entire range
$R=\sp{E_-,E_+}$ of interest for simulation before terminating.
Furthermore, samples at the end of initialization should be numerous
enough to be statistically significant. Given that any samples of
$E_-$ necessarily require first sampling all other energies in $R$ on
the way down from $E_+$, this energy ($E_-$) will generally have the
fewest number of samples. As an end condition, therefore, one can
simply enforce some minimum number of optimistic or pessimistic
samples at $E_-$, i.e. $s_o\p{E_-}$ or $s_p\p{E_-}$. A more
sophisticated end condition would be to choose a minimum temperature
of interest $T_{\t{min}}$ and initialize until the mean fractional
error $\bk{\delta_s}_{E,T_{\t{tmin}}}$ in either of the sample counts
$s_o\p{E}$ or $s_p\p{E}$ reaches some minimum value. These mean errors
are
\begin{align}
  \bk{\delta_s}_{E,T}=\bk{s^{-1/2}}_{E,T}=\sum_Es\p{E}^{-1/2}P\p{E,T}
  =\f{\sum_Es\p{E}^{-1/2}D\p{E}e^{-E/kT}}{\sum_{E'}D\p{E'}e^{-E'/kT}},
  \label{eq:fractional_sample_error}
\end{align}
where we use the fact that the fractional error $\delta_G$ in any
histogram $G$ collected via random Monte Carlo sampling is $G^{-1/2}$.

\subsubsection{The energy range of interest}
\label{sec:min_energy}

Using histogram methods generally requires knowing the energy range of
interest for the system at hand. The Wang-Landau method, for example,
periodically checks a flatness condition $C\sp{H}$ on the energy
histogram $H\p{E}$. In order for such a condition to be well-defined,
it needs have a specified energy range over which to check the
flatness of $H$. While some systems, such as the Ising model, have
well-defined and easily computable energy range, the same is not true
of most systems. In the case of the square-well fluid, not only is the
minimum energy unknown, some energies have such an incredibly low
state density $D\p{E}$ that one cannot reasonably expect to ever
observe them via Monte Carlo, biased or otherwise. We therefore need
to identify an energy range of interest, specified by a maximum and
minimum energies of interest.

Identifying a maximum energy of interest is straightforward: this is
simply the energy $E_+$ at which the density of states $D\p{E}$ is
maximal. Though high energies become more important for determining
system properties $\bk{X}_T$ at higher temperatures, the relative
importance of energies $E>E_+$ to the energy $E_+$ approaches a
maximum as $T\to\infty$. There is therefore a maximum weight $w\p{E}$
which is appropriate to assign energies $E>E_+$ relative to the weight
$w\p{E_+}$, which is namely the ratio of these weights as
$T\to\infty$. As observed in (\ref{eq:inf_temp_weights}), the weight
array becomes flat as $T\to\infty$, which means that the ratio of
$w\p{E>E_+}$ to $w\p{E}$ appropriate for any given temperature $T$
maximally approaches unity. We can therefore always set
$w\p{E>E_+}=w\p{E_+}$, which will ensure that energies $E>E_+$ are not
sampled any more than is necessary for any positive temperature. The
maximum of $D\p{E}$ can be found by simulating without weights for a
short while, after which the energy histogram $H\p{E}$ should be
maximal at $E_+$.

The minimum important energy $E_-$ for a system is less obvious than
$E_+$. Just as finding $E_+$ naturally required using a ``maximal''
temperature $T\to\infty$, determining $E_-$ requires a choice of some
minimum temperature $T_{\t{min}}$. The minimum important energy $E_-$
is then the energy at which the partition function terms
$D\p{E}e^{-E/kT_{\t{min}}}$ are maximal. Lower energy terms grow
increasingly less important with decreasing energy, and are
sufficiently sampled with canonical weights
$w\p{E<E_-}=e^{-E/kT_{\t{min}}}$ to determine any property
$\bk{X}_{T\ge T_{\t{min}}}$. To maximize $D\p{E}e^{-E/kT_{\t{min}}}$,
we need
\begin{align}
  \f{d}{dE}\p{De^{-E/kT_{\t{min}}}}
  =\f{dD}{dE}e^{-E/kT_{\t{min}}}+De^{-E/kT_{\t{min}}}\p{-\f{1}{kT_{\t{min}}}}=0,
  \label{eq:min_E_setup}
\end{align}
which means
\begin{align}
  \f1{D}\f{dD}{dE}=\f{d\ln D}{dE}=\f{1}{kT_{\t{min}}}.
  \label{eq:min_E_condition}
\end{align}
Though we do not always know the density of states $D\p{E}$, in
practice we compute the best available estimate $D\p{E}$ every time we
need to know $E_-$. If we do not find any energy satisfying
(\ref{eq:min_E_condition}), we use the minimum energy the simulation
has ever observed in place of $E_-$ to define our energy range of
interest.

Once we identify an energy $E_-$ satisfying (\ref{eq:min_E_condition})
in an initialization routine for any histogram method, we effectively
forbid transitions to energies $E<E_-$ by tentatively setting weights
$w\p{E<E_-}=e^{-\p{E-E_-}/kT}$ for some temperature $T\ll
T_{\t{min}}$. These weights prevent the initialization routine from
wasting time on energies at which we will override the weight array
after initialization anyways. A special case was made for Wang-Landau,
which was designed assuming knowledge of the energy range of interest
a priori. In order to fairly compare Wang-Landau to other methods, we
therefore identified $E_-$ for each simulated system using other
methods, and hard-coded the minimum important energies for each system
into the Wang-Landau initialization routines\fixme{talk about how bad
  this is}. We always set $w\p{E<E_-}=e^{-\p{E-E_-}/kT}$ after
initialization of all histogram method.

@@

\subsection{Histograms and arrays}

\fixme{Give examples of energy histograms for one system, density of
  states for several $N$, and perhaps a weight array.}

@@

\begin{figure}[H]
  \centering
  \caption[Density of states]{Density of states}
  \label{fig:density_of_states}
\end{figure}

@@

\subsection{Sample rates}

@@

@@

\subsection{Errors in $u$, $c_V$, and $s_{\t{config}}$}

\fixme{Discuss errors in computed thermodynamic properties. Introduce
  Converged flat weights.}

\begin{figure}[H]
  \centering
  \caption[Internal energy]{Specific internal energy}
  \label{fig:u_error}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Heat capacity]{Specific heat capacity}
  \label{fig:cv_error}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Configurational entropy]{Specific configurational
    entropy}
  \label{fig:s_error}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{thesis}
